Analysis of different methods for constructing continuous limits of agreement from smooth biomechanical data

### 2021-09-28 paper.Rmd
Add y-axis range as function argument to plot_loa()

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

@@

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

@@

plot_loa(data, floa.point, floa.roislien, floa.lenhoff)
```

### Leave-one (curve) out cross validation
Displayed are boxes for different calculation methods (FLoA~RCB_v2~, FLoA~RCB_v3~, FLoA~Roislien~, FLoA~Point~)

>>>>

plot_loa(data, floa.point, floa.roislien, floa.lenhoff, ylim = c(-5, 5))
```

@@

plot_loa(data, floa.point, floa.roislien, floa.lenhoff, ylim = c(-10, 10))
```

@@

plot_loa(data, floa.point, floa.roislien, floa.lenhoff, ylim = c(-15, 15))
```

### Leave-one (curve) out cross validation
